\begin{enabstract}
\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

This thesis introduces the design and usage of the \LaTeX{} template for China University of Mining and Technology, Beijing (CUMTB) thesis. The template is based on the ctexbook document class of \LaTeX{}, strictly following the thesis format specifications of CUMTB. The template supports three degree types: bachelor, master, and doctor, providing a complete structure including cover, abstract, table of contents, main text, references, and acknowledgements.

The template provides a complete thesis structure, including cover page, Chinese and English abstracts, table of contents, main body, references, acknowledgements, etc. Basic information of the thesis, such as title, author, school, major, advisor, etc., can be configured through simple commands. The template also supports thesis formats for three degree types: bachelor, master, and doctor.

This template uses the XeLaTeX compilation engine and has good Chinese support. Bibliography management uses biblatex and biber, conforming to the national standard GB/T 7714-2015. The template also integrates commonly used environments for figures, tables, equations, and code, facilitating users to write high-quality academic papers.

By using this template, authors can focus more on writing the content of the thesis without worrying too much about formatting details. The design goals of the template are ease of use, comprehensive functionality, and standard formatting.

\end{enabstract}
